\section{Troubleshooting}

\subsection*{Why is a client unable to connect to the server?}

Some users may see this error message in the Log area:

\begin{quote}
failed to connect to server: address not found for: foobar
\end{quote}

This is usually caused by having no local DNS server. If this is the case, 
you'll need to use an IP address instead.

\subsection*{What port does synergy use?}

By default synergy uses TCP port 24800 but this can be changed.

\subsection*{How do I lock the mouse on one screen?}

This is useful for when playing video games or other full screen applications.
The Scroll Lock key can be used to prevent the mouse switching input to
another screen. Users that don't have a Scroll Lock key can re-assign
the lock key by clicking "Configure Server" and selecting the "Hotkeys" tab.

\subsection*{Why is the mouse over sensitive in games on the client?}

To solve this you need to do two things.

First enable relative mouse movements on the server:
\begin{enumerate}
  \item Click "Configure Server",
  \item Click the "Advanced server settings" tab,
  \item Tick the "Use relative mouse moves" checkbox
  \item Click "OK"
\end{enumerate}

Finally lock the mouse to your client screen
(see: How do I lock the mouse on one screen?).

\subsection*{Why do certain programs stop me from moving the mouse off screen?}

This usually occurs in Vista and above, and is due to UAC in Windows. The
solution to this is to run Synergy in "Service" mode (this can be selected
from the wizard). You can also try launching Synergy as an administrator.

\subsection*{How do I stop synergys from crashing in CentOS?}

Some versions of CentOS (and Red Hat) freeze when the XInitThreads function
is called. To fix this, launch synergy from the command line and use the
--no-xinitthreads argument.

\subsection*{Why do I get "This application has failed to start..." error?}

Windows users may see this error when trying to start Synergy:

\begin{quote}
The application has failed to start because the application configuration is
incorrect. Reinstalling the application may fix the problem.
\end{quote}

This may occur if the Microsoft Visual C++ Redistributable was
removed from your computer. To fix this, please either reinstall Synergy
or download the Redistributable from the Microsoft Downloads website:
http://www.microsoft.com/downloads/

\subsection*{How do I send developers the debug output?}

Click the "Edit" menu and select "Settings". Then change the "Logging level"
drop-down to "Debug" or higher. The debug output should appear in the "Log"
area of the main window (if not, try restarting the program). You are able
to copy text from this area by right clicking.

